\documentclass[class=report,11pt,crop=false]{standalone}
\input{../Style/ChapterStyle.tex}
\begin{document}

\chapter*{Acknowledgements}
\epigraph{When the wind blows in your face, when you feel you are losing your head, when the going gets tough, and when all else fails, look inside you, you are not alone.}
    {\emph{---Malak El Halabi}}
\vspace{0.5cm}

The completion of my degree, represented in the culmination of this project, has only been possible with the love and support surrounding me each step of the way. When reading the above quote, I am overcome with gratitude for all the amazing people in my life. This journey has not been easy, and along the way I have been guided by so many. While I can't personally mention, or even comprehend, the role everyone has played, I would like to thank you \emph{all}. Nevertheless, mentions and gratitude are due.

% Academic
To my academic supervisor, Prof Andrew Wilkinson: thank you for your support and advice throughout this project - no matter the time of day. Your patience and wisdom has guided me, and your knowledge has allowed for this project's completion.  

% Teachers
To my passionate teaches along the way- Mrs Obery, Mrs Steenhoff, Mr Benson, Matt Higginson and Mike Bownes: Thank you for your dedication and commitment. Your belief in me, challenging of me, and the time invested in me is greatly appreciated. You ignited a passion and inspired me to grow. 

% Friends
To my friends and housemates- Colin, Jack, James and Nick: Each one of you has supported and helped me along the way, from rejuvenating and illuminating walks, sound engineering advice and help, encouragement and not least the endless cups of coffee. This year has been significantly easier and more enjoyable with you all by my side.

% Family
To my family: Mom and Dad, you have never waived in your support of, and encouragement for, me. You have sacrificed so much, and given me everything - I am forever grateful and indebted to you for the privilege of education. Your unconditional love is a bedrock in my life. Additional thanks too, for the meticulous proofing of this report. My sister- Danni, thank you for being my closest friend and biggest support. You keep me grounded and honest.

% Becs
And finally, to my best friend, Becs: your constant encouragement, understanding and love is truly a blessing. Thank you for the many laughs, tears and adventures. You make every day brighter with your love for life.
\end{document}